---
title: "Assignment 2"
author: "Drishti"
date: "2023-02-15"
output:
  html_document: default
  pdf_document: default
---

## Question 1 - Creating a linear regression line from a set of vectors
```{r}
# Part A
x<- c(4, 6, 13, 16, 12, 10, 12, 5) 
y<- c(3, 4, 4, 18, 19, 16, 16, 20)

# Part B
library(ggplot2)
data<-data.frame(x,y)
ggplot(data=data,mapping=aes(x,y))+
  geom_point(size=3,color="maroon")

# PART C
data<-data.frame(x,y)
ggplot(data=data,mapping=aes(x,y))+
  geom_point(size=3,color="maroon")+
  geom_smooth(method="auto",alpha=0.1)
```

## Question 2
```{r}
#Extracting the .txt file
data= scan("C:/Users/drish/OneDrive/Desktop/R files/Datasets/Assignments/data.txt",sep=",")
data

# Part A : Creating a horizontal Box plot
boxplot(data, horizontal=TRUE, main= "Horizontal Box Plot", col="maroon")

# Part B: Creating a Horizontal Bar plot


barplot(data,col="steel blue",horiz=TRUE, main="Horizontal Bar Plot") 


```


## Question 3- Creating a Stem and Leaf graph and Histogram
```{r}
# Part A
# creating the required vector
x<- c(3,5,7,5,3,6,8,5,4,5,9,7,4);x

# sorting it out in the decreasiing order
x<- sort(x,decreasing = TRUE); x

# creating a stem and leaf plot
stem(x)

# Part B
# make a score data file and its histogram
score<-scan("C:/Users/drish/OneDrive/Desktop/R files/Datasets/Assignments/score.txt")
hist(score,ylim=c(0,5),col="maroon")
          
```


## Question 4 - Creating Data Strings
```{r}
# creating data strings
x<-c("3","7","9","5");x
Labels<-c("London","New York","Singapore","Mumbai");Labels
class(x)
class(Labels)
A<-c("x: 3 7 9 5",
      "Labels: London New YorK Singapore Mumbai ");A

```


## Question 5 - Scatter plot, Box plot and Pie chart
```{r}
# putting data into a variable "score"
score<- matrix(c(32,40,31,39,50,26,35,38,21,27,12,44,22,45,41,42,46,20,48,45),4,5)
score

# creating a box plot
boxplot(score, col="lavender", main="Box plot of Score data")

# creating a scatter plot of "score"
par(bg= "#E7E8D1")
plot(score, col="darkgreen",pch=20, lwd=6,main="Scatter Blot of Score data")

# creating a pie chart of "score"
pie(score,main="Pie chart of score data", labels=names(score),edges=4)
```


## Question 6 - Creating a matrix and finding its var and median
```{r}
# creating the required matrix
bird<- matrix(c(10,9,37,4,8,18,2,12,1,13,32,23,3,27,4,10),4,4,byrow=TRUE)
bird
row.names(bird)<-c("Parrot","Redtail","Honeybee","Bufftail")
colnames(bird)<-c("Golden","Rain","Yellow","Blackberry")
bird

# converting the above matrix to a list
bird_data<-as.data.frame(bird)
bird_data
# converting into dataframe and then into list as direct conversion is not possible
bird_list<- as.list(bird_data)
bird_list

# Part C
rowMeans(bird)
colMeans(bird)

# Part D
# Median of 1,2,and 4 rows
median(bird[1,])
median(bird[2,])
median(bird[4,])
# variance of the above rows
var(bird[1,])
var(bird[2,])
var(bird[4,])
```


## Question 7- Plotting a PIE chart
```{r}
rain<- read.csv("C:/Users/drish/OneDrive/Desktop/R files/Datasets/Assignments/question6.csv")
rain

pie(rain$Rain.in.cms.,labels=rain$Month, clockwise=FALSE,col= rainbow(12),init.angle=270)
```


## Question 8- Finding cumulative values and other mathematical operators
```{r}
x<- c(5, 1, 3, 7, 9, 0, 1, 5, 8, 2, 10, 15, 2, 21, 9, 15, 3, 20)
# part A
# finding cumulative maximum
cummax(x)

# finding cumulative standard deviation
a=seq_along(x);a
for(i in 1:length(x))
{
  a[i]=sd(1:i)
}
print(a)

# part B 
x2<- c(15,2,0,-1,3,NA,2,9,20)

# finding cumulative length
s= seq_along(na.omit(x2)); s

# finding cumulative sum
cumsum(na.omit(x2))

# part C
asin(0.7071068)*(180/pi)

# part D 
exp(0.6931472)

# part E
factorial(15)
log(0.1,base=5)
```


## Question 9 - Using Summary command
```{r}
# Part A
# Reading the table in R
data_set= read.csv("C:/Users/drish/OneDrive/Desktop/R files/Datasets/Assignments/question9.csv")
data_set

# finding sum and length
attach(data_set)
sum(Count)
sum(Speed)
length(Count)
length(Speed)
detach(data_set)

# part c
# finding a six summary for the dataframe

summary(data_set)
```


## Question 10 - Creating required Dataframe
```{r}
# Part A
# creating a dataframe
height<- c(58,60,61,57,39,59,70,66,65,80)
weight<- c(115,125,120,225,119,159,200,105,146,139)
your_name<- data.frame(height,weight); your_name

# Part B
# adding a vector to the above data frame
category<- c("normal", "normal", "normal","overweight", "normal","overweight", "overweight", "underweight", "overweight", "normal")

your_name<- data.frame(your_name,category)
your_name

# getting a list from the given dataframe

# creating function to divide weight by category
divide_weight_by_category <- function(your_name) {
  categories <- unique(your_name$category)
  weight_acc_category<- lapply(categories, function(x) your_name$weight[your_name$category== x])
  names(weight_acc_category)<- categories
  return(weight_acc_category)
}

weight_acc_category<- divide_weight_by_category(your_name)
weight_acc_category
```

